### 2018-10-13 pkg/colorspace/index.Rmd
completed split-up of colorspace.Rmd which itself has been re-written to give a first quick overview of the package's functionality
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@332 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r ggplot2, echo = FALSE, fig.show = "hide", fig.width = 4.5, fig.height = 4.5, fig.align = "center", dev = "png", dpi = 48}
library("ggplot2")
ggplot(iris, aes(x = Sepal.Length, fill = Species)) + geom_density(alpha = 0.6) + scale_fill_discrete_qualitative()
```

>>>>

```{r ggplot2, echo = FALSE, fig.show = "hide", fig.width = 4.5, fig.height = 4.5, fig.align = "center", dev = "png", dpi = 48}
library("ggplot2")
theme_set(theme_minimal())
ggplot(iris, aes(x = Sepal.Length, fill = Species)) + geom_density(alpha = 0.6) + scale_fill_discrete_qualitative()
```
